
\kapitel{General Information} \label{GeneralInfo}
\thispagestyle{plain}
\renewcommand\section{\stdsection}
\setcounter{section}{1}
\subsection{System Overview}
The ''System Readiness Inspector'' is a PowerShell tool that helps you to check the readiness of a system to detect advanced persistent threats and lateral movement.After the SRI ran successfully it generates a PDF-Document showing wrong or missung configurations. The SRI was developed during a student research project by the two computer science bachelor students Claudio Mattes and Lukas Kellenberger.
\\\\
The SRI has four different modes: Online, Offline, GroupPolicy, AllGroupPolicies. The online mode is limited to the current system and thus determines readiness. The offline mode is used to be able to make a statement about any system by means of exports.
The GroupPolicy mode is limited to a specific Group Policy, which is checked for its
audit settings. In the AllGroupPolicies mode, all group policies of the current domain are examined.

\subsection{Organization of the Manual}
The user manual consists of five parts: General Information, System Overview, Getting Started and Using SRI.
\\\\
The General Information section explains the tool and the purpose for which it is intended.
\\\\
The System Overview section provides a general overview of the system requirements.  Which operating systems are supported, what software must be pre-installed, and what authorizations the user must have.
\\\\
The Getting Started section explains how to obtain and install the SRI on the device. 
\\\\
The Use SRI section provides a detailed description of the system functions. 

